SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-02-07 sedona-ieice16/revision/cover_letter.tex
SEDONA final updates

\opening{Dear Prof. Rajkumar Buyya:}

@@

Attached is a minor revision that responds to the first reviewer's comments. 
We marked in red some text in response to his/her comments. 
The revision also includes some texts marked in blue that are added or updated. 
Note also that we replaced the term of {\em PUT} with another term, called {\em INC}, 
in order to prevent readers from getting confused with a general concept of the program under test. 
Many thanks to you for taking sincere care of our manuscript during a series of reviews.

>>>>

\opening{Dear Editor-in-Chief:}

@@

I am re-submitting a revised manuscript that responds to a previous reviewer's comments. 
I mark in red some text in response to the reviewer's comments. 
This revision also includes some text marked in blue that are added or updated, 
compared to its previous version.

Here are highlights of differences between the revision and the previous version.

\begin{itemize}

\item Research goal: the goal of this manuscript is clearly stated upfront in Section~1.

\item Characteristics: the distinctions of our protocol are discussed 
in the paragraph of ``Characteristics" in Section~1.

\item Timing environment: the description of our timing environment 
is moved upfront to Section~1 (from Section~2), 
to emphasize the fact that even though a timing environment was well configured, 
there still existed significant variability in the traditional measurement method.

\item Terminology: the definition of ``dual-PUT" is provided with its example in Section~2.

\item Experiments: the results from a new experiment are provided in Fig.~5 on page~4.

\end{itemize}

Many thanks to you for handling our manuscript.

### 2017-02-07 sedona-ieice16/revision/paper.tex
SEDONA final updates

We used 128~seconds as the task length and ran the PUT program (termed PUT128) 
800~times. {\color{red}Note that PUT128 was run on a machine, with 
a specification illustrated in Table~\ref{tab:machine_config}, 
in a controlled environment 
with (i)~many non-critical daemon processes deactivated, (ii)~the 
network timing protocol daemon enabled, and (iii)~an up-to-date kernel.}

@@

{\bf Related Work.} 
McGeoch introduced
two basic methods of measuring program time: elapsed time and CPU time~\cite{Mcgeoch12}. 
Bryant and O'Hallaron~\cite{Randal03} 
presented two timing schemes of using clock-cycle and interval counters. 
They proposed a measurement protocol, called {\em minimum-of-k}, 
that for observed elapsed ticks the minimum is chosen as the most accurate one. 
Odom et al.'s work~\cite{Odom05} focused on timing long-running programs 
in a simulation framework via dynamic sampling of trace snippets during program execution. 
None of these prior works, however, takes into account the variability in 
timing and the influence of daemons that may significantly disturb the timing.

@@

{\bf A Running Example.} 
As motivated by our prior work~\cite{Currim}, 
we configure a timing environment by i) stopping non-critical daemons, 
ii) activating the Network Timing Protocol daemon, and 
iii) switching off particular CPU features\cite{intel15,intelSpeed15} if any (Step 1).

>>>>

We used 128~seconds as the task length and ran the PUT program (termed PUT128) 
800~times. {\color{red}Note that PUT128 was run on a machine, with 
a specification illustrated in Table~\ref{tab:machine_config}, 
in the same timing environment as used in our prior work~\cite{Currim}, 
with i)~non-critical daemons deactivated, 
ii)~the Network Timing Protocol daemon switched on,  
iii)~particular CPU features\cite{intel15,intelSpeed15} turned off, and 
and iv)~an up-to-date kernel installed.}

@@

{\bf Related Work.} 
McGeoch introduced
two basic methods of measuring program time: elapsed time and CPU time~\cite{Mcgeoch12}. 
Bryant and O'Hallaron~\cite{Randal03} 
presented two timing schemes of using clock-cycle and interval counters. 
They proposed a measurement protocol, called {\em minimum-of-k}, 
that for observed elapsed ticks the minimum is chosen as the most accurate one. 
Odom et al.'s work~\cite{Odom05} focused on timing long-running programs 
in a simulation framework via dynamic sampling of trace snippets during program execution. 
But none of these prior works considers the variability in 
timing and the impact of daemons that may disturb the timing a lot.

@@

{\bf A Running Example.} 
%As motivated by our prior work~\cite{Currim}, 
%we configure a timing environment by i) stopping non-critical daemons, 
%ii) activating the Network Timing Protocol daemon, and 
%iii) switching off particular CPU features\cite{intel15,intelSpeed15} if any (Step 1). 
{\color{blue}
First, we set up the same measurement environment as described earlier in Section~\ref{sec:intro}, 
to eliminate known timing factors in advance (Step~1).}
